Oral contraceptives

### 2021-01-18 r_notebooks/exploring_hydroxychloroquine_sulphate.nb.Rmd
R analyses

```{r, health-board-modelling}
# plan(multisession)
# with_progress(system.time(hcq_hb_cv_models <-
#   regionalCV(data = hcq_monthly_quantity_hb_pre_cv19)))
# plan(sequential)
# 
# hcq_hb_cv_models %>%
#   saveRDS("../data/hcq_hb_cv_models.rds")

>>>>

```{r, health-board-modelling}
plan(cluster)
with_progress(system.time(hcq_hb_cv_models <-
  regionalCV(data = hcq_monthly_quantity_hb_pre_cv19)))
plan(sequential)

hcq_hb_cv_models %>%
  saveRDS("../data/hcq_hb_cv_models.rds")
